A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-09-14 04_Severity_MetaAnalysis.Rmd
Remove commented code
Format code. Be more specific in GAM model structure

We can fit a gam curve between the 1 - 9 scale and the new scale between 0 and 1
```{r}
# fit a curve using a gam with spline value 0.2
g1 <- gam(x ~ s(y,spar = 0.1))

# View plot of gam
plot(x = predict(g1, data.frame(y= seq(1,9, by =0.1))), y= seq(1,9, by =0.1))
points(x,y,col = "red", pch = 16)

@@

```{r}
# one value is a negative, this should be a zero
# new_sev[12] <- 0

# Allocate new variable percent severity
PM_dat_D$yi_percent <- new_sev

>>>>

We can fit a GAM curve between the 1 - 9 scale and the new scale between 0 and 1.

```{r}
# fit a curve using a gam with spline value 0.01
g1 <- gam(x ~ s(y, spar = 0.1), family = gaussian)

# View plot of gam
plot(x = predict(g1,
                 data.frame(y = seq(1, 9, by = 0.1))), y = seq(1, 9, by = 0.1))
points(x, y, col = "red", pch = 16)

@@

```{r}
# Allocate new variable percent severity
PM_dat_D$yi_percent <- new_sev
